---
title: "Rprogramming"
author: "jojo"
date: "2021/11/29"
output: pdf_document
---

Judge class of object
```{r}
x <- c(4, "a", TRUE) #char
x <- c(4, TRUE) #num
```


If I have two vectors x <- c(1,3, 5) and y <- c(3, 2, 10), what is produced by the expression rbind(x, y)?
a matrix with two rows and three columns
```{r}
x <- c(1,3, 5)
y <- c(3, 2, 10)
rbind(x, y)
```
Similarly, cbind(x,y) returns a matrix with three rows and two columns.

**Dataset: hw1_data**
Extract the last 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
tail(hw1_data, 2)
```

What is the value of Ozone in the 47th row?
```{r}
hw1_data$Ozone[47]
```

How many missing values are in the Ozone column of this data frame?
```{r}
sum(hw1_data$Ozone=="NA") #When NA is char, not empty
```
Otherwise,
```{r}
sum(is.na(hw1_data$Ozone))
```

What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.
```{r}
x <- as.numeric(hw1_data$Ozone[hw1_data$Ozone!="NA"]) #transform char to num to compute mean
mean(x)
```

Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?
```{r}
sub <- subset(hw1_data, hw1_data$Ozone>31 & hw1_data$Temp>90) #use subset()
mean(as.numeric(sub$Solar.R))
```

What was the maximum ozone value in the month of May (i.e. Month is equal to 5)?
```{r}
sub <- subset(hw1_data, hw1_data$Ozone!="NA")
max(as.numeric(sub$Ozone[sub$Month=="5"]))
```





