---
title: "Rprogramming"
author: "jojo"
date: "2021/11/29"
output: pdf_document
---

Judge class of object
```{r}
x <- c(4, "a", TRUE) #char
x <- c(4, TRUE) #num
```


If I have two vectors x <- c(1,3, 5) and y <- c(3, 2, 10), what is produced by the expression rbind(x, y)?
a matrix with two rows and three columns
```{r}
x <- c(1,3, 5)
y <- c(3, 2, 10)
rbind(x, y)
```
Similarly, cbind(x,y) returns a matrix with three rows and two columns.

**Dataset: hw1_data**
Extract the last 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
tail(hw1_data, 2)
```

What is the value of Ozone in the 47th row?
```{r}
hw1_data$Ozone[47]
```

How many missing values are in the Ozone column of this data frame?
```{r}
sum(hw1_data$Ozone=="NA") #When NA is char, not empty
```
Otherwise,
```{r}
sum(is.na(hw1_data$Ozone))
```

What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.
```{r}
x <- as.numeric(hw1_data$Ozone[hw1_data$Ozone!="NA"]) #transform char to num to compute mean
mean(x)
```

Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?
```{r}
sub <- subset(hw1_data, hw1_data$Ozone>31 & hw1_data$Temp>90) #use subset()
mean(as.numeric(sub$Solar.R))
```

What was the maximum ozone value in the month of May (i.e. Month is equal to 5)?
```{r}
sub <- subset(hw1_data, hw1_data$Ozone!="NA")
max(as.numeric(sub$Ozone[sub$Month=="5"]))
```

## Control Structures
if-else
```{r}
if(condition){
  
}else if(condition){
  
}else{
  
}

```

for loop
```{r}
x <- c("a","b","c")
for(i in 1:3){
  print(x[i]) #the three tyoes have same output
}
for(i in seq_along(x)){
  print(x[i])
}
for(letter in x){
  print(letter)
}
```

while loop
```{r}
count <- 10
while(count<10){
  
}
```

repeat (not gennerally used)
Repeat is an infinite loop. The only way to exit a reap loop is to break.
```{r}
reprat{
  
  if(condition){
    break
  }
}
```

next
nest is used to skip an iteration of a loop.
```{r}
for(i in 1:100){
  if(i<20){
    next
  }
  # do something else
}
```

return
returen signals that a function should exit and return a given value.

## Function
```{r}
add2 <- function(x,y){ #use function() to write a funciton
  x+y
}
add2(3,5)
```
Write a more complicated one.
```{r}
above <- function(x,n){ #x is a sequence; can set default value n=10
  use <-x>n
  x[use]
}
x<- 1:20
above(x,12)
```
```{r}
columnmean <- function(y, removeNA=TRUE){
  nc <- ncol(y)
  means <- numeric(nc) #initialize a vector of length nc
  for(i in 1:nc){
    means[i] <- mean(y[,i], na.rm=removeNA) #remove na
  }
  means
}
columnmean(airquality)
```


